RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-07 doc/paper.tex

   \subsection{Iterated local search}
    Iterated local search (ILS)~\cite{lourencco2003iterated} is an efficient meta-heuristics, whose essential idea is given as follow. Iteratively generate a sequence of solutions generated by the (embedded) heuristic, such as local search or  randomized greedy heuristics,  leading
    towards better solutions than if one uses repeated random trials of that heuristic. This simple idea appeared in the literature by Baxter~\cite{baxter1981local} in early 1980s, and, since then, had been many time re-invented by many researches under different names; some of the following names were used: iterated descent search~\cite{baum1998iterated}, large-step
    Markov chains~\cite{martin1991large}, chained local optimization~\cite{martin1996combining}, or, in some cases,  combinations of these~\cite{applegate2003chained}.

@@

An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by LS procedure. At each iteration, ILS applies three steps. First, the current incumbent solution is perturbed, that is mutated in a way the knowledge of the current best solution is (partially) used at the next iterations.  Secondly, the perturbed solution is then improved by LS procedure. Thirdly, the LS outcome is thereafter compared to the incumbent solution and possibly replaced as the new one, with accordance to the chosen acceptance criterion.

@@

>>>>

  \subsection{Iterated local search}
    Iterated local search (ILS)~\cite{lourencco2003iterated} is an efficient meta-heuristics, whose essential idea is given as follow. Iteratively generate a sequence of solutions produced by the (embedded) heuristic, such as local search or  randomized greedy heuristics,  leading
    towards better solutions than if one uses repeated random trials of that heuristic. This simple idea appeared in the literature by Baxter~\cite{baxter1981local} in early 1980s, and, since then, had been many time re-invented by many researches under different names; some of the following names were used: iterated descent search~\cite{baum1998iterated}, large-step
    Markov chains~\cite{martin1991large}, chained local optimization~\cite{martin1996combining}, or, in some cases,  combinations of these~\cite{applegate2003chained}.

@@

An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by LS procedure. At each iteration, ILS applies three steps. First, the current incumbent solution is perturbed, that is mutated in a way the knowledge of the current best solution is (partially) used at the next iterations.  Secondly, the perturbed solution is then improved by LS procedure. Thirdly, the LS outcome is thereafter compared to the incumbent solution and the search us possibly moved to the new solution, with accordance to the chosen acceptance criterion. Usually, this basic variant of ILS incorporates a mechanism of tabu list, that avoids the search getting back to already visited local search within a number of iterations.

@@

 \\
